Title here

### 2016-09-21 portfolio/text/ms.Rmd
Add refs

Natural resources such as forests, land animals, and fishes
provide a primary source of income for millions of people worldwide [REFS].
However, environmental,
biological, and price variation
combined with regulatory changes
and human-caused environmental disasters
generate high levels of income variability and risk
for these individuals.
For example, drought and flooding are major sources of risk 
to agricultural food security 
(http://rstb.royalsocietypublishing.org/content/360/1463/2139.short),
And EVOS example

@@

- crop rotation has been proposed as metric for buffering against short term
  variation and long term trends (like climate change)
- BUT in some situations, external forces (prices, demand) may discourage the
  adoption of these diverse strategies and help promote specialization, 
http://link.springer.com/article/10.1007/s10584-004-0710-z

@@

This effect has been identified for fisheries.
At community level, ... [@sethi2014]
At vessel level, ... [@kasperski2013] ...
- Eric: Most papers on fisheries have adopted the approach similar to Kasperski et
al. and used data reported to the level of vessels or higher. This analysis
is unique in that we're able to separate individual people from vessels
(enabling us to track people that switch fishery sectors over time, or
change strategies and utilize multiple vessels)

@@

Our models focused on species diversity
as a possible predictor of revenue and revenue variability
while controlling for effort.
We calculated effective species diversity for
permit holder $i$ and time (year) $t$ as the inverse of
Simpson's diversity index 
(TODO - Jost 2006; also referred to in economics as the Herfindahl-Hirschman Index) 
$\lambda$ [@simpson1949]
weighted by revenue $R$ ('species diversity') 
*Eric: (also say we did this for consistency with previous analyses,e.g. Kasperski and Holland):*

@@

The general framework of our model is known as a variance function
regression model, which separately models change in the mean and variance as
a function of covariates (TODO - Davidian and Carrol 1987
http://amstat.tandfonline.com/doi/abs/10.1080/01621459.1987.10478543; Hall
and Carrol 1989, http://www.jstor.org/stable/2345837). Where traditional
linear models or hierarchical linear models generally assume constant
variance, the variance function regression model allows variance to be
heteroskedastic. For application to economic data on individual fishing
portfolios, this type of model allows certain strategies and levels of
diversification to be more or less variable than others.

>>>>

Natural resources such as forests, land animals, and fishes
provide a primary source of income for millions of people worldwide [REFS].
However, environmental,
biological, and price variation
combined with regulatory changes
and human-caused environmental disasters
generate high levels of income variability and risk
for these individuals.
For example, drought and flooding are major sources of risk 
to agricultural food security [@gregory2005],
And EVOS example

@@

- crop rotation has been proposed as metric for buffering against short term
  variation and long term trends (like climate change)
- but in some situations, external forces (prices, demand) may discourage the
  adoption of these diverse strategies and 
  help promote specialization [@bradshaw2004]

@@

This effect has been identified for fisheries.
At community level, ... [@sethi2014]
At vessel level, ... [@kasperski2013] ...
- Eric: Most papers on fisheries have adopted the approach similar to @kasperski2013 and used data reported to the level of vessels or higher. This analysis
is unique in that we're able to separate individual people from vessels
(enabling us to track people that switch fishery sectors over time, or
change strategies and utilize multiple vessels)

@@

Our models focused on species diversity
as a possible predictor of revenue and revenue variability
while controlling for effort.
For consistency with previous analyses [e.g. @kasperski2013],
we calculated effective species diversity for
permit holder $i$ and time (year) $t$ as the inverse of
Simpson's diversity index $\lambda$
(\citeauthor{simpson1949} \citeyear{simpson1949},
\citeauthor{jost2006} \citeyear{jost2006};
also referred to in economics as the Herfindahl-Hirschman Index)
weighted by revenue $R$:

@@

The general framework of our model is known as a variance function
regression model, which separately models change in the mean and variance as
a function of covariates [e.g. @davidian1987; @hall1989]. Where traditional
linear models or hierarchical linear models generally assume constant
variance, the variance function regression model allows variance to be
heteroskedastic. For application to economic data on individual fishing
portfolios, this type of model allows certain strategies and levels of
diversification to be more or less variable than others.
